Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-04-12 paper/AlignedIsotropicGW.tex
Fix #3 and Fix #9

\acrodef{BBH}{binary black hole}
\acrodef{BH}{black hole}
\acrodef{EM}{electromagnetic}
\acrodef{GW}{gravitational wave}
\acrodef{PE}{parameter estimation}

@@

Figure \ref{fig:O1-posteriors} shows an approximation to the posterior
inferred on $\chieff$ for the three likely \ac{GW} detections
GW150914, GW151226 and LVT151012 from \citet{O1-BBH}.  Because samples
drawn from the posterior on $\chieff$ are not publicly released at
this time, we have approximated the posterior as a Gaussian
distribution with the same mean and 90\% credible interval as quoted
in \citet{O1-BBH}.  Since all three mergers involve black holes of
comparable masses, there is essentially no posterior support for both
black holes' $\chi \gtrsim 0.5$, in contrast to the majority of the
electromagnetically-detected stellar-mass black hole population (see
Section \ref{sec:discussion}).  The analysis here is relatively
insensitive to the precise details of the posterior distributions;
other conclusions are more sensitive.  In particular, our Gaussian
approximation does permit $\chieff = 0$ for GW151226 while the true
posterior rules this out at high confidence
\citep{2016PhRvL.116x1103A,O1-BBH}.

\begin{figure}
  \plotone{../plots/chi-eff-mock-posteriors}
  \caption{\label{fig:O1-posteriors} Approximate posteriors on
    $\chieff$ from the LIGO O1 observations in \citet{O1-BBH}.  We
    approximate the posteriors reported in \citet{O1-BBH} using
    Gaussians with the same median and 90\% credible interval as
    reported in \citet{O1-BBH}.  It is notable that none of the
    $\chieff$ posteriors extends to the regime of high spin magnitudes
    inferred from several electromagnetically-detected stellar-mass
    black hole systems (see \citet{2015PhR...548....1M} for a summary
    of such measurements).}
\end{figure}

>>>>

\acrodef{BBH}{binary black hole}
\acrodef{BH}{black hole}
\acrodef{EM}{electromagnetic}
\acrodef{GW}{gravitational wave}
\acrodef{O1}{first observing}
\acrodef{PE}{parameter estimation}

@@

Figure \ref{fig:O1-posteriors} shows an approximation to the posterior
inferred on $\chieff$ for the three likely \ac{GW} detections
GW150914, GW151226 and LVT151012 from Advanced LIGO's first observing
run (O1) \citep{O1-BBH}.  Because samples drawn from the posterior on
$\chieff$ are not publicly released at this time, we have approximated
the posterior as a Gaussian distribution with the same mean and 90\%
credible interval as quoted in \citet{O1-BBH}.  Since all three
mergers involve black holes of comparable masses, there is essentially
no posterior support for both black holes' $\chi \gtrsim 0.5$, in
contrast to the majority of the electromagnetically-detected
stellar-mass black hole population (see Section \ref{sec:discussion}).
The analysis here is relatively insensitive to the precise details of
the posterior distributions; other conclusions are more sensitive.  In
particular, our Gaussian approximation does permit $\chieff = 0$ for
GW151226 while the true posterior rules this out at high confidence
\citep{2016PhRvL.116x1103A,O1-BBH}.

\begin{figure}
  \plotone{../plots/chi-eff-mock-posteriors}
  \caption{\label{fig:O1-posteriors} Approximate posteriors on
    $\chieff$ from the Advanced LIGO O1 run observations in
    \citet{O1-BBH}.  We approximate the posteriors reported in
    \citet{O1-BBH} using Gaussians with the same median and 90\%
    credible interval as reported in \citet{O1-BBH}.  It is notable
    that none of the $\chieff$ posteriors extends to the regime of
    high spin magnitudes inferred from several
    electromagnetically-detected stellar-mass black hole systems (see
    \citet{2015PhR...548....1M} for a summary of such measurements).}
\end{figure}
